Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by organization x.}

### 2018-08-15 paper.tex
PRISM for Agent 1

\lstinputlisting[caption=Controls., captionpos=b, language=Big,
label=agent1_controls, firstline=3, lastline=14]{models/agent1.big}

@@

\lstinputlisting[caption=Predicates and the initial state., captionpos=b,
language=Big, label=agent1_code, firstline=16,
lastline=30]{models/agent1.big}

@@

\lstinputlisting[caption=The action of going north., captionpos=b,
language=Big, label=agent1_north, firstline=88,
lastline=117]{models/agent1.big}

@@

\lstinputlisting[caption=Reaction rule to stay home if a required number of
objects is acquired., captionpos=b, language=Big, label=agent1_home,
firstline=186, lastline=189]{models/agent1.big}

>>>>

\lstinputlisting[caption=Controls., captionpos=b, language=Big,
label=agent1_controls, firstline=3, lastline=14]{models/agent1/agent.big}

@@

\lstinputlisting[caption=Predicates and the initial state., captionpos=b,
language=Big, label=agent1_code, firstline=16,
lastline=30]{models/agent1/agent.big}

@@

\lstinputlisting[caption=The action of going north., captionpos=b,
language=Big, label=agent1_north, firstline=88,
lastline=117]{models/agent1/agent.big}

@@

\lstinputlisting[caption=Reaction rule to stay home if a required number of
objects is acquired., captionpos=b, language=Big, label=agent1_home,
firstline=186, lastline=189]{models/agent1/agent.big}
